Papers

### 2025-04-28 papers.qmd
bugfix

## Invited Talks
"Bayesian Model Calibration: An Elastic Approach" *Colorado State Univeristy Statistics Seminar*, April 28, 2025, [Slides](https://jdtuck.github.io/presentations/CSU_April25/CSU_April25.html)

>>>>

## Invited Talks
"Bayesian Model Calibration: An Elastic Approach" *Colorado State University Statistics Seminar*, April 28, 2025, [Slides](https://jdtuck.github.io/presentations/CSU_April25/CSU_April25.html)
